{\bf \normalsize Title}

### 2024-10-06 slides/literature-xiaohui.tex
revise proposal slides

  Here are some definitions needed: 
    \begin{itemize}
    \item response variable $y \in \mathbb R$
    \item explanatory variable $\bx \in \mathbb R^p$
    \item set of environments $\mathcal E$
    \item observations from environment $e\in \mathcal E$:
      $(\bx_1^{(e)}, y_1^{(e)}), \dots,  (\bx_n^{(e)}, y_n^{(e)}) \sim \mu^{(e)}$
    \end{itemize}

@@

\begin{frame}
  \frametitle{Model Formulation}
  The true linear model is assumed as
  \begin{align}
    \label{main_eq}
    y^{(e)} = (\bm\beta^*_{S^*})^\top \bx_{S^*}^{(e)} + \varepsilon^{(e)} ~~~~~ \text{with} ~~~~ \mathbb{E}[\varepsilon^{(e)}|\bx_{S^*}^{(e)}] \equiv 0,
  \end{align} where the unknown set of important variables $S^* = \{j: \beta_j^* \neq 0\}$ and the model parameters $\bm \beta^*$ are the same across different environments, while $\mu^{(e)}$, the distribution of $(\bx^{(e)},y^{(e)})$, may vary.

@@

  The aim is to estimate $\bm\beta^*$ and $S^*$ using the $n\cdot |\mathcal{E}|$ data $\{(\bx_i^{(e)}, y_i^{(e)})\}_{e\in \mathcal{E}, i\in \{1,\ldots, n\}}$.
\end{frame}

@@

\begin{frame}
  \frametitle{Loss Function}
  The population-level EILLS objective is 
  \begin{scriptsize}
  \begin{align}
    \mathsf{Q}_\gamma(\bm\beta) &= \underbrace{\sum_{e\in \mathcal{E}} \mathbb{E} \left[|y^{(e)} - \bm\beta^\top \bx^{(e)}|^2\right]}_{\mathsf{R}(\bm\beta)} \nonumber\\
                                &\qquad + \gamma \underbrace{\sum_{j=1}^p \mathbf{1}\{\beta_j\neq 0\} \times  \sum_{e\in \mathcal{E}}  \left|\mathbb{E} [(y^{(e)} - \bm\beta^\top \bx^{(e)}) x_j^{(e)}]\right|^2}_{\mathsf{J}(\bm\beta)},
  \end{align}
  \end{scriptsize}
  where $\gamma$ is a tuning parameter.
  \begin{itemize}
  \item $\mathsf R(\bm\beta)$ requires a good overall solution in each single environment.
  \item $\mathsf J(\bm\beta)$ discourages selecting variables that have strong correlation with the fitted residuals in some environments.
  \item From computational perspective, we have
    \begin{align}
    \mathsf{J}(\bm \beta) &= \sum_{j=1}^p \mathbf{1}\{\beta_j \neq 0\} \sum_{e\in \mathcal{E}} \frac{1}{4} |\nabla_j \mathsf{R}^{(e)}(\bm\beta)|^2,
  \end{align}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Empirical Loss Function}
  \begin{align*}
    \hat{\mathsf{J}}(\bm\beta) &= \sum_{j=1}^p \mathbf{1}\{\beta_j \neq 0\} \sum_{e\in \mathcal{E}}  \left| \hat{\mathbb{E}}[x_j^{(e)} (y^{(e)} - \bm\beta^\top \bx^{(e)})]\right|^2\\
    \hat{\mathsf{R}}(\bm\beta)& = \sum_{e\in \mathcal{E}}  \frac{1}{n^{(e)}} \sum_{i=1}^{n^{(e)}} \{ y^{(e)}_i - \bm\beta^\top \bx^{(e)}_i \}^2\\
    \hat{\mathsf{Q}}(\bm\beta,\gamma) &= \hat{\mathsf{R}}(\bm\beta) + \lambda \hat{\mathsf{J}}(\bm\beta)
  \end{align*}
  Some linear exogenous variables which do not contribute to explaining $y$ can
  be eliminated further by introducing an $l_0$ penalty as
    \begin{align*}
   \hat{\mathsf{L}}(\bm\beta,\gamma,\lambda) =  \hat{\mathsf{R}}(\bm\beta) + \lambda \hat{\mathsf{J}}(\bm\beta) + \lambda \|\bm\beta\|_0.
  \end{align*}
\end{frame}

\begin{frame}
  \frametitle{An Illustration}
  \begin{figure}[H]
      \centering \includegraphics[width=0.8\textwidth]{figs/example}
      \caption{An Example for Illustration, figure from \cite{fan2023environmentinvariantlinearsquares}}
    \end{figure}
\end{frame}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "template"
%%% End:

>>>>

  Here are some definitions needed: 
    \begin{itemize}
    \item response variable $y \in \mathbb R$
    \item explanatory variable $\bm x \in \mathbb R^p$
    \item set of environments $\mathcal E$
    \item observations from environment $e\in \mathcal E$:
      $(\bm x_1^{(e)}, y_1^{(e)}), \dots,  (\bm x_n^{(e)}, y_n^{(e)}) \sim \mu^{(e)}$
    \end{itemize}

@@

\begin{frame}
  \frametitle{Model Formulation}
  The true linear model is assumed as
  \begin{align}
    \label{main_eq}
    y^{(e)} = (\bm\beta^*_{S^*})^\top \bm x_{S^*}^{(e)} + \varepsilon^{(e)} ~~~~~ \text{with} ~~~~ \mathbb{E}[\varepsilon^{(e)}|\bm x_{S^*}^{(e)}] \equiv 0,
  \end{align} where the unknown set of important variables $S^* = \{j: \beta_j^* \neq 0\}$ and the model parameters $\bm \beta^*$ are the same across different environments, while $\mu^{(e)}$, the distribution of $(\bm x^{(e)},y^{(e)})$, may vary.

@@

  The aim is to estimate $\bm\beta^*$ and $S^*$ using the $n\cdot |\mathcal{E}|$ data $\{(\bm x_i^{(e)}, y_i^{(e)})\}_{e\in \mathcal{E}, i\in \{1,\ldots, n\}}$.
\end{frame}

@@

\begin{frame}
  \frametitle{Loss Function}
  The population-level EILLS objective is 
  \begin{scriptsize}
  \begin{align*}
    \mathsf{Q}_\gamma(\bm\beta) &= \underbrace{\sum_{e\in \mathcal{E}} \mathbb{E} \left[|y^{(e)} - \bm\beta^\top \bm x^{(e)}|^2\right]}_{\mathsf{R}(\bm\beta)} \nonumber\\
                                &\qquad + \gamma \underbrace{\sum_{j=1}^p \mathbf{1}\{\beta_j\neq 0\} \times  \sum_{e\in \mathcal{E}}  \left|\mathbb{E} [(y^{(e)} - \bm\beta^\top \bm x^{(e)}) x_j^{(e)}]\right|^2}_{\mathsf{J}(\bm\beta)},
  \end{align*}
  \end{scriptsize}
  where $\gamma$ is a tuning parameter.
  \begin{itemize}
  \item $\mathsf R(\bm\beta)$ requires a good overall solution in each single environment.
  \item $\mathsf J(\bm\beta)$ discourages selecting variables that have strong correlation with the fitted residuals in some environments.
  \item From computational perspective, we have
    \begin{align*}
    \mathsf{J}(\bm \beta) &= \sum_{j=1}^p \mathbf{1}\{\beta_j \neq 0\} \sum_{e\in \mathcal{E}} \frac{1}{4} |\nabla_j \mathsf{R}^{(e)}(\bm\beta)|^2,
  \end{align*}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Empirical Loss Function}
  \begin{align*}
    \hat{\mathsf{J}}(\bm\beta) &= \sum_{j=1}^p \mathbf{1}\{\beta_j \neq 0\} \sum_{e\in \mathcal{E}}  \left| \hat{\mathbb{E}}[x_j^{(e)} (y^{(e)} - \bm\beta^\top \bm x^{(e)})]\right|^2\\
    \hat{\mathsf{R}}(\bm\beta)& = \sum_{e\in \mathcal{E}}  \frac{1}{n^{(e)}} \sum_{i=1}^{n^{(e)}} \{ y^{(e)}_i - \bm\beta^\top \bm x^{(e)}_i \}^2\\
    \hat{\mathsf{Q}}(\bm\beta,\gamma) &= \hat{\mathsf{R}}(\bm\beta) + \lambda \hat{\mathsf{J}}(\bm\beta)
  \end{align*}
  Some linear exogenous variables which do not contribute to explaining $y$ can
  be eliminated further by introducing an $l_0$ penalty as
    \begin{align*}
   \hat{\mathsf{L}}(\bm\beta,\gamma,\lambda) =  \hat{\mathsf{R}}(\bm\beta) + \lambda \hat{\mathsf{J}}(\bm\beta) + \lambda \|\bm\beta\|_0.
  \end{align*}
\end{frame}

\begin{frame}
  \frametitle{An Illustration}
  \begin{figure}[H]
      \centering \includegraphics[width=0.8\textwidth]{figs/example}
      \caption{An Example for Illustration, figure from \cite{fan2023environmentinvariantlinearsquares}}
    \end{figure}
\end{frame}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal"
%%% End:
